Amendments Summary

### 2025-01-03 Thesis/amend_v2.qmd
update Section 3.2.1
update summary

I will include a discussion on this point in the manuscript currently being prepared for the peer-reviewed journal. **XXX I think you need to add a sentence like this to the thesis too.**

@@

This is indeed a valid inference setting and aligns with common practices in applications where findings from exploratory data analysis (EDA) are subsequently verified using statistical testing. The use of visual methods, such as the lineup protocol, during EDA can help identify potential violations before formal testing.

However, this approach introduces the risk of multiple testing problems, as the data is effectively "double-dipped"—first for hypothesis generation and then for formal testing. Addressing this issue requires careful consideration of selective inference frameworks. Potential solutions include splitting the data into separate subsets for EDA and hypothesis testing or using techniques like cross-validation to ensure robust inference.

This hybrid approach represents an interesting direction for future research, particularly in developing methods to make valid inferences while leveraging the strengths of both visual and formal analysis techniques.

**XXX Not sure if this is a good answer here. The main purpose of avoiding the human evaluation is to reduce the work required of humans. So while it is a potentially good idea to have this hybrid approach the problem is that it won't be adopted because it is too time-consuming. traditional tests are often done because its a click on a software interface or a simple line of code. While making a lineup is typically a simple line of code, too, it requires the additional work of staring at a page of plots to assess if one can determine a difference. So I don't think that you need to respond in the way you have done. But you do need to state how you modified your thesis or why not modify it.**

>>>>

I have updated Section 3.2.1 to include a discussion of this approach.

@@

This is indeed a valid inference setting and aligns with common practices in applications where findings from exploratory data analysis (EDA) are followed by formal statistical testing. Using visual methods, such as the lineup protocol, during EDA can help identify potential violations before formal testing.

However, this approach introduces the risk of multiple testing problems, as the data is effectively "double-dipped" - first for hypothesis generation and then for formal testing. Addressing this issue requires careful attention to selective inference frameworks. Possible solutions include splitting the data into distinct subsets for EDA and hypothesis testing or employing techniques like cross-validation to maintain robust inference.

That said, the primary challenge with this hybrid approach is its potential lack of practicality in many real-world scenarios. The goal of avoiding human evaluation is to minimize the workload for analysts. While the lineup method can be implemented with a simple line of code, it requires the additional effort of visually inspecting multiple plots, which can be time-consuming. In contrast, traditional tests are often preferred because they are easier to apply — typically requiring just a few lines of code or clicks in software interfaces.

As a result, this hybrid approach, while conceptually sound, may not be widely adopted due to its higher demands on time and effort. Given these considerations, I have not modified my thesis to incorporate this approach, as its practical feasibility is limited.
